\Title

### 2020-02-05 manuscript/manuscript.tex
Improve caption of depth type figure

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{Cartoon illustrating the different depth types.}
    \label{fig:depth-types}
\end{figure*}

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/depth_types.pdf}
    \caption{
        Depth types for locating point sources. We put one source beneath each
        observation point (station) using: (a)~a \emph{constant depth} where all sources
        are located at the same depth, (b)~a \emph{relative depth} where all sources are
        located at the same vertical distance from its corresponding observation point,
        and (c)~a \emph{variable relative depth} where the depth of the sources is
        proportional to the average distance to its neighbour sources. Notice how the
        clustered sources on (c) are relatively shallower than the other ones.
    }
    \label{fig:depth-types}
\end{figure*}
